To do

### 2021-09-14 analysis/todo_list.Rmd

- ~~Sum $\rho$ and $\gamma$.~~
- ~~Meta-analyzed binned results across sexes.~~ 
- ~~Fix variance calculation mistake in calculating $\rho$ and $\gamma$.~~
- ~~Write script/function which replaces `Neale_ID` with trait description.~~
- Clean up `index.Rmd`
- Clean up `about.Rmd`
- Add Rmd building to `targets` pipeline. 
- MVMR. 
- AM MR summary Rmd.
- PC correlation among couples summary Rmd. 
- Clean up update meeting Rmd.

>>>>

- ~~Sum $\rho$ and $\gamma$.~~
- ~~Meta-analyzed binned results across sexes.~~ 
- ~~Fix variance calculation mistake in calculating $\rho$ and $\gamma$.~~
- ~~Write script/function which replaces `Neale_ID` with trait description.~~
- ~~Clean up `index.Rmd`~~
- ~~Clean up `about.Rmd`~~
- Add Rmd building to `targets` pipeline. 
- MVMR. 
- AM MR summary Rmd.
- PC correlation among couples summary Rmd. 
- Clean up update meeting Rmd.
